%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{upquote}
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}
{
  \vspace{-4pt}\scshape\raggedright\large
}
{}{0em}{}
[\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}


\newcommand{\resumeSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
      \end{tabular*}
      \textit{\small#3}
}

\newcommand{\resumeMiniheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=6pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, topsep=0ex]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Weichen Ke} & Email: weichenzero@gmail.com\\
  http://darkforte.github.io & Mobile: +86 185-1184-1030 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \begin{itemize}[leftmargin=*, itemsep=-2pt]
    \resumeSubheading
      {Peking University, Ph.D. student}{2016.09 -- Present}
      {GPA: 3.85/4.0, TA of Algorithm Analysis and Complexity Theories}
    \resumeSubheading
      {Beijing University of Technology, Bachelor in Computer Science}{2012.09 -- 2016.07}
      {GPA: 3.93/4.0, Rank: 1/44, TOEFL: 112 (Speaking 26), GRE: 329+4.5 (Q 170)}
  \end{itemize}
    
  %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Didi Research}{2017.07 -- Present}
      {Research Intern at Big Data Strategy Group}
      \resumeItemListStart
        \resumeItem
        {Designed a strategy of order dispatching with reinforcement learning, which boosted \$20k in daily total driver income and 3\% in order finish rate in simulations.}
        \resumeItem
        {Designed and trained a DQN with Keras and learned a value function estimator for order-driver pairs.}
        \resumeItem
        {Constructed pipeline of spatiotemporal features using Hive on PySpark.}
        \resumeItem
        {Organized and presented several company-wide tutorials on deep RL topics like A3C, TRPO, and DDPG etc.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Microsoft Research Asia}{2015.07 -- 2016.07}
      {Research Intern at Software Analytics Group}
      \resumeItemListStart
        \resumeItem 
        {Leader of project BigIn4, the big data analyzing backend of Quick Insights in Microsoft Power BI.}
        \resumeItem
        {Proposed a novel algorithm for interactive approximate query processing on big data based on Tree Augmented Bayesian Network, and implemented it on Spark with Scala and Java.}
        \resumeItem
        {Deployed the platform to production cluster running on Hadoop, and analyzed more than 1TB data per day.}
        \resumeItem
        {Constructed preprocessing pipeline for complex structural data with SparkSQL.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publication}
  \resumeItemListStart
    \resumeItem 
    {Qingwei Lin, \textbf{Weichen Ke}, Jian-Guang Lou, Hongyu Zhang, Kaixin Sui, Yong Xu, Ziyi Zhou, Bo Qiao, Dongmei Zhang. "BigIN4: Instant, Interactive Insight Identification for Multi-Dimensional Big Data", In Proceedings of \textbf{SIGKDD} 2018 (Submitted) }
  \resumeItemListEnd

%-----------AWARDS-----------------
\section{Awards}
  \begin{itemize}[leftmargin=*, itemsep=-12pt]
    \resumeMiniheading{"Star of Tomorrow" Title {\normalfont(For MSRA interns with outstanding performance)}}{2016}
    \resumeMiniheading{Silver Medal of EC-Final Round of ACM-ICPC contest}{2015}
    \resumeMiniheading{IBM Scholarship and National Scholarship {\normalfont(For top 3 students in the dept.)}}{2013 -- 2014}
    \resumeMiniheading{Global Rank 18/1000\texttt{+}, China Rank 2/50\texttt{+} in IEEExtreme Programming Contest}{2013}
    \resumeMiniheading{Meritorious Winner of MCM}{2013}
  \end{itemize}

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeMiniheading{Flappy Bird AI based on Deep Reinforcement Learning with Raw Pixels Input}{2017.06}
        \resumeItemListStart
            \resumeItem {Designed the network architecture (combined actor and value convolution network) with Tensorflow.}
            \resumeItem {Implemented A3C algorithm from scratch, with asynchronous exploration and model updating using Python.}
            \resumeItem {Applied frame stacking and background removal that leads to faster convergence and better results.}
        \resumeItemListEnd
        {\small The AI achieved human-level performance after self-playing for 4 hours on a single GPU.}
    
    \resumeMiniheading{Parameter Server based on C\texttt{++} and MPI}{2017.06}
        \resumeItemListStart
            \resumeItem {Designed the master-coordinator-worker architecture and the communication protocol with Protobuf.}
            \resumeItem {Implemented the architecture with MPI that supports adding/removing workers dynamically.}
            \resumeItem {Implemented sparse parameter transmission to reduce messaging overhead.}
        \resumeItemListEnd
        {\small The PS can train 1 million parameters with 2GB data in 20 seconds with 4 workers running on 4 machines.}
        
    \resumeMiniheading{Real-time Online Game: “Bomber Man Online” on C\texttt{++} and Direct2D}{2015.04}
        \resumeItemListStart
            \resumeItem {Designed messaging protocol under IOCP and managed development process with Git.}
            \resumeItem {Implemented the game core from scratch and efficient game data access using STL with Visual Studio.}
            \resumeItem {Implemented lockstep multiplayer synchronization model with a mutex based thread scheduler.}
        \resumeItemListEnd
        {\small The game runs steadily at 60 fps and achieved synchronized gameplay experience among players.}
        
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
