%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{upquote}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{makecell}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}
{
  \vspace{-4pt}\scshape\raggedright\large
}
{}{0em}{}
[\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4
      \end{tabular*}
}

\newcommand{\resumeSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
      \end{tabular*}
      \textit{\small#3}
}

\newcommand{\resumeMiniheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=6pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, topsep=0ex]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Weichen Ke} & weichenzero@gmail.com\\
  www.linkedin.com/in/weichenzero/ & (412) 482-8717 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \begin{itemize}[leftmargin=*, itemsep=0pt, label={}]
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{Carnegie Mellon University - School of Computer Science } & {Pittsburgh, PA} \\
      \textit{Master of Science, Computer Science | QPA: 4.0/4.33} & {08/2018 -- 12/2019} \\
      \textit{Selected Courses: Parallel Computing, Adv.Database Systems, Adv.Cloud Computing} & {}
    \end{tabular*}
      
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Peking University - School of EECS} & {Beijing, China} \\
    \textit{Ph.D. (Unfinished) | GPA: 3.85/4.0} & {09/2016 -- 06/2018} \\
    \textit{Topics of Interest: Deep Reinforcement Learning, Blockchain} & {}
\end{tabular*}
    
    \resumeEducationHeading
      {Beijing University of Technology - College of Computer Science}{Beijing, China}
      {\textit{Bachelor, Computer Science | GPA: 3.93/4.0, Rank: 1/44}} {09/2012 -- 07/2016}
  \end{itemize}
    
  %\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \begin{itemize}[leftmargin=*, itemsep=5pt, label={}]

    \resumeSubheading
      {Dropbox}{05/2019 -- 08/2019}
      {Software Engineer Intern | Distributed Database, Go, Protobuf, gRPC}
      \resumeItemListStart
        \resumeItem
        {Designed long-running simulation tests for a distributed transactional key-value store database for checking ACID properties, serializability, and two-phase committing. The tests uncovered several major design bugs.}
        \resumeItem
        {Implemented the simulation framework with Go and deployed it in the CI framework and stage cluster.}
    \resumeItemListEnd

    \resumeSubheading
      {Didi Chuxing}{07/2017 -- 07/2018}
      {Algorithm Research Intern | Reinforcement Learning, Python, PySpark, Hive}
      \resumeItemListStart
        \resumeItem
        {Designed a reinforcement learning based order dispatching strategy with Deep Q Network and pushed it online, which boosted GMV by 0.5\% - 5\% in all experimental cities.}
        \resumeItem
        {Built an automated feature visualization pipeline with Hive on PySpark.}
    \resumeItemListEnd
      
    \resumeSubheading
      {Microsoft Research Asia}{07/2015 -- 07/2016}
      {Research Intern | Approximate Query Processing, Scala, Java, Spark}
      \resumeItemListStart
        \resumeItem
        {Proposed a novel algorithm for interactive approximate query processing on big data based on Bayesian Network.}
        \resumeItem
        {Built the asynchronous big data query answering engine for the system on Spark with Scala and Java.}
        \resumeItem
        {Deployed the platform to production cluster running on Hadoop and analyzed more than 1TB data per day.}
        \resumeItem
        {Published the work \href{http://www.kdd.org/kdd2018/accepted-papers/view/bigin4-instant-interactive-insight-identification-for-multi-dimensional-big}{"BigIN4: Instant, Interactive Insight Identification for Multi-Dimensional Big Data"} in SIGKDD 2018 as the 2nd author and the 1st student author.}
      \resumeItemListEnd
  \end{itemize}
  
%-----------PROJECTS-----------------
\section{Projects}
  \begin{itemize}[leftmargin=*, itemsep=5pt, label={}]
    \resumeSubheading{TerrierDB}{06/2019}
    {Carnegie Mellon University | C++, Concurrency Control, Wire Protocol}
    \resumeItemListStart
        \resumeItem {Implemented a B+Tree index with fine-grained latch crabbing to reduce contention in index scans.}
        \resumeItem {Built the networking layer and the traffic cop that fully supports the PostgreSQL wire protocol.}
    \resumeItemListEnd
    
    \resumeSubheading {Low Poly Style Image/Video Transformer} {12/2018}
    {Carnegie Mellon University | C++, CUDA, Computer Graphics}
    \resumeItemListStart
        \resumeItem {Implemented a lock-free Delauney Triangulation algorithm on GPU with CUDA to maximize paralellism, which achieved 50x speedup over the CPU version.}
    \resumeItemListEnd
    
    \resumeSubheading{Parameter Server for Logistic Regression}{06/2017}
    {Peking University | C++, MPI, Protobuf}
        \resumeItemListStart
            \resumeItem {Designed the computation model with MPI and the communication protocol with Protobuf.}
            \resumeItem {Implemented sparse parameter transmission to reduce messaging overhead.}
        \resumeItemListEnd
        
  \end{itemize}

%-----------AWARDS-----------------
\section{Honors}
  \begin{itemize}[leftmargin=*, itemsep=-1pt, label={}]
    \resumeMiniheading{"Star of Tomorrow" Title for outstanding MSRA interns \normalfont{(Rate: 10\%)}}{2016}
    \resumeMiniheading{Silver Medal of EC-Final Round of ACM-ICPC}{2015}
  \end{itemize}

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \begin{itemize}[leftmargin=*, itemsep=-2pt, label={}]
    \item{
      \textbf{Programming Languages}{: C\texttt{++}, Java, Python, Scala, Go}
    }
    \item{
      \textbf{Framework \& Libraries}{: Hadoop, Spark, Hive, Tensorflow, Keras, XGBoost, Protobuf, Git, Linux}
    }
  \end{itemize}


%-------------------------------------------
\end{document}
